Data- and Systems Paper: Identifying Handicap Parking Spots for Event's Venues

### 2016-04-07 milestone1/paper/paper.tex
Added files via upload

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{listings}
\lstset{language=SQL,morekeywords={PREFIX,java,rdf,rdfs,url}}

@@

\subsection{Theaters Dataset}
% TODO describe theaters dataset (fields, contained data, semantics)
The theaters dataset contains the following fields:

\begin{center}
	\begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c |}
		\hline
		\textbf{Trcid} & \textbf{Title} & \textbf{Shortdescription} & \textbf{Longdescription} & \textbf{Calendarsummary} & \textbf{TitleEN} & \textbf{ShortdescriptionEN} & \textbf{LongdescriptionEN} & \textbf{CalendarsummaryEN } & \textbf{Types} & \textbf{Ids} & \textbf{Locatienaam} & \textbf{City} & \textbf{Adres} & \textbf{Zipcode} & \textbf{Latitude } & \textbf{Latitude} & \textbf{Urls} & \textbf{Media} & \textbf{Thumbnail} & \textbf{Datepattern\_startdate} & \textbf{Datepattern\_enddate} & \textbf{Singledates} & \textbf{Type1} & \textbf{Lastupdated} \\ \hline

		\hline
	\end{tabular}
\end{center}

\subsection{Museums and Galleries Dataset}
% TODO describe museums and galleries dataset

\subsection{Handicap's Parking Slots Dataset}
% TODO describe this dataset

>>>>

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{multicol}
\lstset{language=SQL,morekeywords={PREFIX,java,rdf,rdfs,url}}

@@

\subsection{Theaters, Museums and Galleries Dataset}
The theaters and museums dataset contains the same features according to the JSON we used:

\begin{center}
	\textbf{\emph{Features}}
	\setlength{\columnsep}{6em}
\begin{multicols}{3}
	\begin{enumerate}
		\item \textbf{Trcid}
		\item \textbf{Title}
		\item \textbf{Shortdescription}
		\item \textbf{Longdescription}
		\item \textbf{Calendarsummary}
		\item \textbf{TitleEN}
		\item \textbf{ShortdescriptionEN }
		\item \textbf{LongdescriptionEN  }
		\item \textbf{CalendarsummaryEN       }
		\item \textbf{Types} 
		\item \textbf{Ids}
		\item \textbf{Locatienaam}
		\item \textbf{City}
		\item \textbf{Adres}
		\item \textbf{Zipcode}
		\item \textbf{Latitude}
		\item \textbf{Longitude}
		\item \textbf{Urls}
		\item \textbf{Media}
		\item \textbf{Thumbnail}
		\item \textbf{Datepattern\_startdate}
		\item \textbf{Datepattern\_enddate}
		\item \textbf{Singledates}
		\item \textbf{Type1}
		\item \textbf{Lastupdated}			
		\end{enumerate}
\end{multicols}
\end{center}

\subsection{Handicap's Parking Slots Dataset}
\begin{center}
	\textbf{\emph{Features}}
	\setlength{\columnsep}{4em}
	\begin{multicols}{2}
		\begin{enumerate}
			\item \textbf{Adres}
			\item \textbf{Location}
			\item \textbf{Aantal}
			\item \textbf{Onderbord}
			\item \textbf{Stadsdeel}	
			\item \textbf{Locatie-info}				
		\end{enumerate}
	\end{multicols}
\end{center}
